%-------------------------
% YOUR CONTACT INFORMATION
%-------------------------
\contactline{
\textbf{Ahmad Fahrezi} \\
\href{mailto:ahmadfahrezi.kl@gmail.com}{ahmadfahrezi.kl@gmail.com} $|$ 
\href{https://ahmadfahrezi.vercel.app/}{ahmadfahrezi.vercel.app} $|$ 
\href{https://www.linkedin.com/in/ahmadfahrezi}{linkedin.com/in/ahmadfahrezi}
}

\vspace{0.3in}

%-------------------------
% DATE
%-------------------------
April 5, 2024

%-------------------------
% RECIPIENT ADDRESS
%-------------------------
Atome Financial  
Talent Acquisition Team  
10 Anson Road, #20-06 International Plaza  
Singapore 079903

%-------------------------
% SALUTATION
%-------------------------
Dear Hiring Manager,

%-------------------------
% OPENING PARAGRAPH
%-------------------------
Your work enabling flexible payment options through Atome Financial's web platform caught my attention—offering consumers  \$0 interest now-finance-later solutions at checkout mirrors trends I tackled at CommerceOwl. After architecting feature-rich React applications with over 95\%  test coverage, I see clear opportunities to streamline Atome's frontend performance and user flow in your Web Engineer (Frontend) role.

%-------------------------
% BODY PARAGRAPH 1
%-------------------------
At CommerceOwl, I led a team to build a Next.js storefront where I wrote TypeScript components and styled them using CSS3 and styled-components, boosting monthly conversions by 32\% . I established and participated in code reviews, adopting consistent naming conventions and accessibility checks that reduced UI defects by 40\% . Collaborating daily with designers and product managers honed my ability to translate Figma prototypes into pixel-perfect, responsive interfaces.

%-------------------------
% BODY PARAGRAPH 2
%-------------------------
My analytical approach extends beyond UI code. Implementing advanced SEO strategies lifted organic traffic by 50\%  in six months at CommerceOwl, and integrating performance budgets shaved initial load times by 25\% . These experiences underline my focus on clean, scalable code and fast, user-friendly pages—an asset when optimizing Atome's multi-tenant dashboards.

%-------------------------
% BODY PARAGRAPH 3
%-------------------------
Though my formal title was Frontend Engineer, I routinely conducted peer reviews to maintain code quality and foster skill sharing across React, TypeScript, and CSS. I enjoy tackling nuanced UI challenges—from fluid grids for mobile checkout to modular SCSS layouts—that ensure consistency and accessibility at scale.

%-------------------------
% CLOSING PARAGRAPH
%-------------------------
I welcome the chance to discuss how my blend of React expertise, TypeScript rigor, CSS know-how, and code review experience can advance Atome Financial's frontend vision. Thank you for considering my application—I look forward to connecting.

%-------------------------
% SIGNATURE
%-------------------------
\signaturespace

Sincerely,  

Ahmad Fahrezi