%-------------------------
% RESUME CONTENT FILE
%-------------------------

%-------------------------
% HEADER SECTION
%-------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ahmadfahrezi.vercel.app/}{\Large Ahmad Fahrezi}} & \small\href{mailto:ahmadfahrezi.kl@gmail.com}{ahmadfahrezi.kl@gmail.com}\\
  \small \href{https://ahmadfahrezi.vercel.app/}{ahmadfahrezi.vercel.app} & \small\href{https://www.linkedin.com/in/ahmadfahrezi}{linkedin.com/in/ahmadfahrezi} \\
\end{tabular*}

%-------------------------
% TECHNICAL SKILLS SECTION
%-------------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, Java, SQL, PHP} \\
     \textbf{Frameworks}{: React, Next.js, React Native, Node.js, Spring Boot, Vue.js, Remix} \\
     \textbf{Testing \& Automation}{: Appium, Selenium, Jest, Pytest, Test Planning, QA Automation, Postman} \\
     \textbf{Tools}{: Git, Docker, Firebase, AWS (EC2, S3), GitHub Actions, Jenkins, Figma, Supabase} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Oracle, Prisma, Firebase Realtime DB} \\
     \textbf{Other}{: REST APIs, Authentication (JWT, OAuth, SSO), CI/CD, Agile/Scrum, SEO Optimization, RBAC} }}
 \end{itemize}

%-------------------------
% EXPERIENCE SECTION
%-------------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern – QA Automation}{July 2024 -- Dec. 2024}
      {Grab}{Petaling Jaya, MY}
      \resumeItemListStart
        \resumeItem{Spearheaded development of an AI-powered test automation agent, eliminating manual scripting overhead for authentication workflows and accelerating test development by 60\%.}
        \resumeItem{Delivered 22 production-grade Python automation scripts using Appium and Selenium frameworks, exceeding H2 2024 automation coverage targets by 15\% for Grab's Identity platform.}
        \resumeItem{Executed critical weekly regression test suites ensuring platform stability and security for 200+ million Grab users across 8 Southeast Asian markets.}
        \resumeItem{Validated REST APIs using Postman and SQL; tracked 40+ bugs including 8 critical security issues.}
        \resumeItem{Collaborated cross-functionally with product managers and engineers to define test strategies for new features.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Frontend Developer}{Oct. 2022 -- Feb. 2024}
      {CommerceOwl}{Edmonton, CA (remote)}
      \resumeItemListStart
        \resumeItem{Architected and delivered feature-rich web applications across multiple JavaScript ecosystems with 95\%+ test coverage using Jest and React Testing Library.}
        \resumeItem{Drove 32\% increase in conversion rates for RecipeStack Shopify app through strategic UI/UX improvements and performance optimizations.}
        \resumeItem{Collaborated with backend teams to integrate RESTful APIs and optimize data fetching patterns, reducing client-side data requests by 45\%.}
      \resumeItemListEnd

   \resumeSubheading
      {Software Engineer Intern}{July 2023 -- Oct. 2023}
      {UM PTM}{Kuala Lumpur, MY}
      \resumeItemListStart
        \resumeItem{Instrumental in modernizing UM's legacy procurement system, building a full-stack web application using PHP MVC architecture and MySQL.}
        \resumeItem{Engineered robust server-side validation layer in PHP with MySQL constraints and triggers, preventing data corruption.}
        \resumeItem{Collaborated with stakeholders across 5 departments in Agile sprints to gather requirements and deliver modular, maintainable code.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------
% PROJECTS SECTION
%-------------------------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading{TeaPOS -- Multi-Tenant Point-of-Sale Platform}{https://github.com/ahmadfahrezi81/tea-pos}{Next.js 14, TypeScript, Supabase, PostgreSQL, Tailwind, Chart.js, shadcn/ui}
          \resumeItemListStart
            \resumeItem{Architected enterprise-grade, multi-tenant SaaS POS system supporting isolated data management for unlimited organizations with tenant-scoped users.}
            \resumeItem{Engineered normalized Supabase schema with 12+ relational tables implementing row-level security policies for bulletproof data isolation.}
            \resumeItem{Built responsive admin dashboard leveraging Next.js 14 App Router and React Server Components for real-time sales visualization.}
            \resumeItem{Implemented granular role-based access control (RBAC) with store-level permissions using Supabase Auth.}
          \resumeItemListEnd
       \resumeProjectHeading{Eco-Mobility Tracker}{https://github.com/ahmadfahrezi81/Eco-Mobility-Mobile-App}{React Native, Next.js, TypeScript, Redux, Firebase, Expo, Google Maps API}
          \resumeItemListStart
            \resumeItem{Engineered cross-platform mobile application tracking real-time carbon footprints using GPS sensors and machine learning-based transport mode detection.}
            \resumeItem{Designed hybrid system architecture combining React Native client with Next.js SSR dashboard for scalable data analytics.}
            \resumeItem{Integrated Google Maps Platform APIs for interactive route visualization and carbon emission heatmaps.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------
% EDUCATION SECTION
%-------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, MY}
      {Bachelor of Computer Science, Software Engineering}{Oct. 2021 -- Oct. 2025}
    \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Data Structures \& Algorithms, Database Systems, Object-Oriented Design \& Implementation, Mobile App Development, Machine Learning, Web Development, Software Engineering Principles}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
