%-------------------------
% RESUME CONTENT FILE (UPDATED)
%-------------------------

%-------------------------
% HEADER SECTION
%-------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ahmadfahrezi.vercel.app/}{\Large Ahmad Fahrezi}} & \small\href{mailto:ahmadfahrezi.kl@gmail.com}{ahmadfahrezi.kl@gmail.com}\\
  \small \href{https://ahmadfahrezi.vercel.app/}{ahmadfahrezi.vercel.app} & \small\href{https://www.linkedin.com/in/ahmadfahrezi}{linkedin.com/in/ahmadfahrezi} \\
\end{tabular*}

%-------------------------
% TECHNICAL SKILLS SECTION
%-------------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript (ES6+), TypeScript, HTML/CSS, Python, Dart} \\
     \textbf{Frameworks  \&  Libraries}{: React, Next.js, Tailwind CSS, Redux Toolkit, Zustand, TanStack Query, Storybook} \\
     \textbf{Testing  \&  QA}{: Jest, Cypress, Playwright, Testing Library} \\
     \textbf{DevOps  \&  Cloud}{: GitHub Actions, Vercel, Netlify, Docker, CI/CD Pipelines} \\
     \textbf{Tools}{: Figma, Notion, Agile/Scrum, SEO, Accessibility (WCAG), Core Web Vitals} }}
 \end{itemize}

%-------------------------
% EXPERIENCE SECTION
%-------------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern – QA Automation}{July 2024 -- Dec. 2024}
      {Grab}{Petaling Jaya, MY}
      \resumeItemListStart
        \resumeItem{Accelerated test development by 60\%  via AI-powered Appium  \&  Selenium automation agent.}
        \resumeItem{Delivered 22 Python scripts, surpassing coverage targets by 15\%  for identity workflows.}
        \resumeItem{Integrated regression suites into GitHub Actions CI/CD, reducing feedback cycles by 80\% .}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer}{Oct. 2022 -- Feb. 2024}
      {CommerceOwl}{Edmonton, CA (remote)}
      \resumeItemListStart
        \resumeItem{137\%  organic traffic growth via SEO  \&  Core Web Vitals optimizations on ImagineAPI (Next.js).}
        \resumeItem{Cut page-load time by 40\%   \&  boosted Shopify app conversions by 32\%  through React  \&  A/B tests.}
        \resumeItem{Integrated CI/CD with GitHub Actions  \&  Vercel to slash release cycles by 80\% .}
        \resumeItem{Built TypeScript component library with Storybook, reducing UI redundancy by 25\% .}
        \resumeItem{Delivered responsive, accessible interfaces achieving 95\% + Lighthouse scores via WCAG best practices.}
        \resumeItem{Reduced network requests by 45\%  partnering with backend teams on API consumption.}
      \resumeItemListEnd

   \resumeSubheading
      {Software Engineer Intern}{July 2023 -- Oct. 2023}
      {UM PTM}{Kuala Lumpur, MY}
      \resumeItemListStart
        \resumeItem{Modernized procurement UI in PHP  \&  MySQL, streamlining workflows for 500+ staff.}
        \resumeItem{Implemented RBAC  \&  server-side validation to enforce audit compliance and data security.}
        \resumeItem{Built reporting dashboard reducing manual report time by 70\%  with real-time analytics.}
        \resumeItem{Documented deployment on Apache  \&  Git, improving maintainability for IT teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------
% PROJECTS SECTION
%-------------------------
\section{Projects}
    \resumeSubHeadingListStart

       \resumeProjectHeading{TeaPOS -- Multi-Tenant POS Platform}{https://github.com/ahmadfahrezi81/tea-pos}{Next.js 14, TypeScript, Supabase, PostgreSQL, Tailwind CSS}
          \resumeItemListStart
            \resumeItem{Architected multi-tenant Next.js app with RLS  \&  role-based permissions for isolated data.}
            \resumeItem{Reduced transaction latency by 35\%  via offline caching  \&  optimized React hooks.}
            \resumeItem{Built serverless REST APIs on Vercel Edge with OpenAPI specs, enhancing contract clarity.}
            \resumeItem{Automated CI/CD with GitHub Actions  \&  Vercel to ensure zero-downtime deployments.}
          \resumeItemListEnd

       \resumeProjectHeading{Eco-Mobility Tracker}{https://github.com/ahmadfahrezi81/Eco-Mobility-Mobile-App}{React Native, Next.js, TypeScript, Firebase, Expo}
          \resumeItemListStart
            \resumeItem{Optimized GPS batching in React Native, cutting battery usage by 28\%  while retaining 99\%  sync reliability.}
            \resumeItem{Developed SSR analytics dashboard in Next.js for route insights  \&  emission summaries.}
            \resumeItem{Implemented offline state management with Redux  \&  persistent storage for uninterrupted tracking.}
            \resumeItem{Integrated Google Maps APIs for route visualization  \&  eco-friendly suggestions.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-------------------------
% EDUCATION SECTION
%-------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, MY}
      {Bachelor of Computer Science (Software Engineering)}{Oct. 2021 -- Aug. 2025}
    \resumeItemListStart
        \resumeItem{\textbf{CGPA}: 3.7 / 4.0 · \textbf{Dean’s List (2022–2024)}}
        \resumeItem{\textbf{Relevant Coursework}: Data Structures  \&  Algorithms, Web Development (Spring Boot, PHP, React), Database Systems, Software Engineering Principles}
        \resumeItem{\textbf{Awards}: Winner – Sustainability FYP@UM 2023 · 3rd Place – CodeNection Hackathon 2022}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
