%-------------------------
% COVER LETTER CONTENT FILE - MASTER TEMPLATE
% 
% LLM MODIFICATION INSTRUCTIONS:
% This master positions Ahmad as a full-stack engineer with backend/systems depth.
% Target: 150-200 words for final output
% 
% TAILORING STRATEGY:
% 1. Select 1-2 most relevant experiences from the options below
% 2. Match technical stack mentions to job requirements
% 3. Adjust tone: startups = "ship fast", enterprise = "scalable systems"
% 4. Replace [Job Title], [Company Name], and [specific hook] with real details
% 5. Use placeholders: __APOS__ __AMP__ __PCT__ __HASH__ __DOLLAR__
% 6. Keep all LaTeX commands and braces balanced
%-------------------------

%-------------------------
% YOUR CONTACT INFORMATION
%-------------------------
\contactline{
\textbf{Ahmad Fahrezi} \\
\href{mailto:ahmadfahrezi.kl@gmail.com}{ahmadfahrezi.kl@gmail.com} $|$ 
\href{https://ahmadfahrezi.vercel.app/}{ahmadfahrezi.vercel.app} $|$ 
\href{https://www.linkedin.com/in/ahmadfahrezi}{linkedin.com/in/ahmadfahrezi}
}

\vspace{0.3in}

%-------------------------
% SALUTATION
%-------------------------
Dear Hiring Manager,

%-------------------------
% OPENING PARAGRAPH (2 sentences)
% Direct hook: role + top relevant qualification
%-------------------------
I__APOS__m applying for the [Job Title] role at [Company Name]. I build full-stack systems that handle real user load—at Grab, I shipped automation infrastructure supporting 200+ million users, and at CommerceOwl, I engineered web apps that drove measurable revenue growth.

%-------------------------
% BODY PARAGRAPH - OPTION A: Backend/Systems Focus
% Use for: Backend Engineer, Platform Engineer, Infrastructure roles
% Highlights: Database design, system architecture, scalability
%-------------------------
At UM PTM, I redesigned a legacy procurement system into a modular PHP application backed by a normalized MySQL schema with 15+ relational tables. I implemented RBAC, server-side validation, and audit logging to handle 500+ staff workflows. Later, I built TeaPOS, a multi-tenant SaaS platform using Next.js and PostgreSQL with row-level security, isolated tenant data, and serverless APIs on Vercel Edge—architecture decisions that directly impact reliability at scale.

%-------------------------
% BODY PARAGRAPH - OPTION B: Full-Stack Focus
% Use for: Full-Stack Engineer, Software Engineer (general), Product Engineer roles
% Highlights: End-to-end ownership, performance, user impact
%-------------------------
At CommerceOwl, I owned frontend and backend for multiple production apps. I increased RecipeStack__APOS__s conversion rate by 32__PCT__ through performance optimization (40__PCT__ faster load times) and A/B testing. For ImagineAPI, I built the entire stack—Next.js frontend, Node.js backend, and Stripe integration—serving 200+ paying subscribers. I reduced API response times by 45__PCT__ through request batching and implemented CI/CD pipelines that cut release cycles by 80__PCT__.

%-------------------------
% BODY PARAGRAPH - OPTION C: QA/Automation Focus
% Use for: QA Engineer, SDET, Test Automation roles
% Highlights: Testing infrastructure, CI/CD, reliability
%-------------------------
At Grab, I built an AI-powered test automation agent that eliminated manual scripting for authentication workflows, cutting test development time by 60__PCT__. I delivered 22 production-ready Python scripts using Appium and Selenium, integrated them into CI/CD pipelines via GitHub Actions, and created an internal dashboard (Python + Allure) to track coverage metrics. I identified 40+ bugs (8 critical) before they reached production, ensuring platform stability across 8 markets.

%-------------------------
% BODY PARAGRAPH - OPTION D: Versatility/Cross-Functional
% Use for: Startup roles, roles requiring multiple skills
% Highlights: Breadth across QA, frontend, backend
%-------------------------
My experience spans the full development cycle. I__APOS__ve built test automation at Grab (Python, Selenium, CI/CD integration), shipped high-traffic frontends at CommerceOwl (React, Next.js, 95+ Lighthouse scores), and architected backend systems with PostgreSQL, Docker, and serverless APIs. I move between QA, frontend, and backend work depending on what the product needs—whether that__APOS__s debugging a flaky test, optimizing a slow query, or designing a new API endpoint.

%-------------------------
% CLOSING PARAGRAPH (1-2 sentences)
% Direct, confident call to action
%-------------------------
I__APOS__d welcome the chance to discuss how I can contribute to [Company Name]__APOS__s engineering team. Let__APOS__s connect.

%-------------------------
% SIGNATURE
%-------------------------
\signaturespace

Sincerely,

Ahmad Fahrezi