%-------------------------
% RESUME CONTENT FILE (UPDATED)
%-------------------------

%-------------------------
% HEADER SECTION
%-------------------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ahmadfahrezi.vercel.app/}{\Large Ahmad Fahrezi}} & \small\href{mailto:ahmadfahrezi.kl@gmail.com}{ahmadfahrezi.kl@gmail.com}\\
  \small \href{https://ahmadfahrezi.vercel.app/}{ahmadfahrezi.vercel.app} & \small\href{https://www.linkedin.com/in/ahmadfahrezi}{linkedin.com/in/ahmadfahrezi} \\
\end{tabular*}

%-------------------------
% TECHNICAL SKILLS SECTION
%-------------------------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript (ES6+), TypeScript, Java, PHP, SQL, HTML/CSS, C/C++, Dart, Go} \\
     \textbf{Frameworks \& Libraries}{: React, Next.js, React Native, Node.js, Express, Vue.js, Remix, Spring Boot, Tailwind CSS, Redux Toolkit, Zustand, Prisma, Zod, Axios, Chart.js, shadcn/ui, TanStack Query, Expo} \\
     \textbf{Testing \& QA}{: Selenium, Appium, Jest, Pytest, Cypress, Playwright, Postman, JUnit, Allure Reports, API \& E2E Testing, Test Planning, Regression Automation} \\
     \textbf{DevOps \& Cloud}{: Docker, GitHub Actions, Firebase, Supabase, AWS (EC2, S3, Lambda), Vercel, Netlify, Nginx, Jenkins, CI/CD Pipelines, Monitoring (Sentry, Datadog)} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Oracle, SQLite, Redis, Firestore, Firebase Realtime DB} \\
     \textbf{APIs \& Integrations}{: REST, GraphQL (basic), JWT, OAuth 2.0, SSO, RBAC, WebSockets, Stripe, Shopify, Google Maps, Cloudinary, OpenAI API} \\
     \textbf{Tools \& Practices}{: Git, Jira, Trello, Figma, Notion, Agile/Scrum, TDD, SOLID, Clean Architecture, SEO, Accessibility (WCAG)} }}
 \end{itemize}

%-------------------------
% EXPERIENCE SECTION
%-------------------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern – QA Automation}{July 2024 -- Dec. 2024}
      {Grab}{Petaling Jaya, MY}
      \resumeItemListStart
        \resumeItem{Spearheaded development of an AI-powered test automation agent, eliminating manual scripting overhead for authentication workflows and accelerating test development by 60\%.}
        \resumeItem{Delivered 22 production-grade Python automation scripts using Appium and Selenium, exceeding automation coverage targets by 15\% for Grab’s Identity platform.}
        \resumeItem{Collaborated across 3 squads with PMs, designers, and engineers to define comprehensive test strategies for iOS and Android authentication features.}
        \resumeItem{Executed weekly regression suites ensuring platform stability and security for 200+ million users across 8 Southeast Asian markets.}
        \resumeItem{Integrated automated regression tests into CI/CD pipelines via GitHub Actions, enabling continuous test execution and faster defect feedback cycles.}
        \resumeItem{Developed internal test reporting dashboard (Python + Allure) to visualize coverage metrics and build health, reducing manual reporting by 80\%.}
        \resumeItem{Identified and documented 40+ bugs (8 critical), improving user trust and reliability.}
        \resumeItem{Designed and maintained detailed test plans, cases, and automation frameworks under Agile best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {Frontend Developer}{Oct. 2022 -- Feb. 2024}
      {CommerceOwl}{Edmonton, CA (remote)}
      \resumeItemListStart
        \resumeItem{Engineered and shipped high-impact web applications across React, Next.js, Remix, and Vue.js, delivering scalable, maintainable frontends for SaaS and e-commerce clients.}
        \resumeItem{Boosted RecipeStack Shopify app conversion rates by 32\% through UI/UX revamp, A/B testing, and page-load optimization (–40\% load time).}
        \resumeItem{Designed and launched \textbf{ImagineAPI} (Next.js + Node.js), a production-grade image generation service serving 200+ active subscribers.}
            \resumeItemListStart
                \resumeItem{Conducted 50+ user interviews to guide feature roadmap and improve developer experience (78\% satisfaction).}
                \resumeItem{Implemented advanced SEO and Core Web Vitals strategies (dynamic sitemaps, structured metadata), driving 137\% organic traffic growth and improving search ranking from position \#5 → \#2.}
            \resumeItemListEnd
        \resumeItem{Developed internal TypeScript component library with Storybook to unify design patterns across multiple frontends and reduce UI redundancy by 25\%.}
        \resumeItem{Integrated CI/CD pipelines via GitHub Actions + Vercel for automated testing and preview deployments, cutting release cycles by 80\%.}
        \resumeItem{Partnered with backend teams to optimize REST API consumption, reducing network requests by 45\% and improving data load efficiency.}
        \resumeItem{Collaborated closely with designers and PMs in Agile sprints to deliver pixel-perfect, responsive, and accessible interfaces (95+ Lighthouse accessibility scores).}
      \resumeItemListEnd

   \resumeSubheading
      {Software Engineer Intern}{July 2023 -- Oct. 2023}
      {UM PTM}{Kuala Lumpur, MY}
      \resumeItemListStart
        \resumeItem{Modernized UM’s legacy procurement system into a modular PHP MVC + MySQL web application, streamlining requisition and approval workflows for 500+ staff.}
        \resumeItem{Designed normalized database schema with 15+ relational tables handling requisitions, approvals, vendors, and purchase orders; enforced data integrity via foreign keys and constraints.}
        \resumeItem{Engineered robust validation layers and server-side security checks ensuring full policy and audit compliance.}
        \resumeItem{Implemented role-based access control (RBAC) and session management to safeguard confidential procurement data.}
        \resumeItem{Built real-time reporting dashboard for transaction and approval tracking, reducing manual reporting time by 70\%.}
        \resumeItem{Deployed system on Apache with Git version control and documented deployment procedures for internal IT maintenance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------
% PROJECTS SECTION
%-------------------------
\section{Projects}
    \resumeSubHeadingListStart

       \resumeProjectHeading{Job Bot -- AI-Powered Job Application Pipeline}{https://github.com/ahmadfahrezi81/job-bot}{FastAPI, Celery, Redis, OpenAI GPT-4, Crawl4AI, Playwright, Supabase, LaTeX, Docker}
          \resumeItemListStart
            \resumeItem{Engineered an end-to-end asynchronous job pipeline for intelligent extraction, evaluation, and document generation.}
            \resumeItem{Built a FastAPI microservice with Celery + Redis for concurrent job processing across 8 pipeline stages.}
            \resumeItem{Integrated GPT-4 for job-fit scoring, resume tailoring, and natural-language cover letter generation.}
            \resumeItem{Combined Crawl4AI and Playwright with LLM fallbacks for high-reliability job scraping across diverse boards.}
            \resumeItem{Automated LaTeX-based resume/cover letter generation and Supabase upload with public CDN links.}
            \resumeItem{Designed duplicate-detection and smart filtering (Notion API), cutting false positives by 40\%.}
            \resumeItem{Deployed with Docker Compose, achieving <30s average processing time and 95\% uptime.}
          \resumeItemListEnd

       \resumeProjectHeading{TeaPOS -- Multi-Tenant Point-of-Sale Platform}{https://github.com/ahmadfahrezi81/tea-pos}{Next.js 14, TypeScript, Supabase, PostgreSQL, Tailwind, Chart.js, shadcn/ui}
          \resumeItemListStart
            \resumeItem{Architected a multi-tenant SaaS POS platform with isolated tenant data, role-based permissions, and real-time analytics.}
            \resumeItem{Designed a secure Supabase backend with 12+ relational tables, row-level security (RLS), and store-level RBAC policies.}
            \resumeItem{Developed serverless REST APIs on the Vercel Edge network and documented backend contracts using OpenAPI specs.}
            \resumeItem{Implemented modular, scalable architecture with shared UI libraries, reusable hooks, and type-safe Zod validation across layers.}
            \resumeItem{Built mobile-optimized POS interfaces with offline caching, reducing transaction latency by 35\%.}
            \resumeItem{Created custom analytics dashboards using Chart.js and React hooks for live sales and revenue insights.}
            \resumeItem{Automated CI/CD pipelines via GitHub Actions and Vercel for seamless testing, migrations, and deployments.}
            \resumeItem{Authored technical documentation and schema guidelines to support maintainability.}
          \resumeItemListEnd

       \resumeProjectHeading{Eco-Mobility Tracker}{https://github.com/ahmadfahrezi81/Eco-Mobility-Mobile-App}{React Native, Next.js, TypeScript, Redux, Firebase, Expo, Google Maps API}
          \resumeItemListStart
            \resumeItem{Built a cross-platform mobility tracker estimating carbon emissions using ML-based transport mode detection from GPS and accelerometer data.}
            \resumeItem{Developed a React Native client integrated with a Next.js SSR analytics dashboard for insights, user profiles, and route history.}
            \resumeItem{Designed a Firebase backend for authentication, geolocation, and emission data aggregation.}
            \resumeItem{Implemented Redux state management and offline caching for reliable background tracking.}
            \resumeItem{Optimized GPS batching and data compression, reducing battery usage by 28\% while maintaining 99\% sync reliability.}
            \resumeItem{Integrated Google Maps APIs for route visualization, emission heatmaps, and eco-route suggestions.}
            \resumeItem{Automated CI/CD pipelines with Expo EAS and GitHub Actions for streamlined Android/iOS deployments.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-------------------------
% EDUCATION SECTION
%-------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, MY}
      {Bachelor of Computer Science (Software Engineering)}{Oct. 2021 -- Aug. 2025}
    \resumeItemListStart
        \resumeItem{\textbf{CGPA}: 3.7 / 4.0 · \textbf{Dean’s List (2022–2024)}}
        \resumeItem{\textbf{Relevant Coursework}: Data Structures \& Algorithms, Database Systems (Oracle, MySQL, MongoDB), Object-Oriented Design \& Implementation, Mobile App Development (Android), Machine Learning (TensorFlow), Web Development (Spring Boot, PHP, React), Software Engineering Principles}
        \resumeItem{\textbf{Awards}: Winner – Sustainability FYP@UM 2023 · 3rd Place – CodeNection Hackathon 2022}
    \resumeItemListEnd
  \resumeSubHeadingListEnd